---
title: "Course Project"
output: pdf_document
---
================================================

Let's simulate the exponential distribution! We have 40 samples, each with **lambda** values of 0.2. Let's run this with 2500 trials (simulations).

```{r}
set.seed(12312412) # random seed
library(ggplot2) # plotting 

lambda <- 0.2
n_samples <- 40 
n_sims <- 2500
mu <- apply(matrix(rexp(n_samples*n_sims, lambda), n_sims), 1, mean) # sample means
mean_mu <- mean(mu) # mean of sample means
mu_theor <- 1/lambda # theoretical mean
var_mu <- var(mu) # variance of sample means
var_theor <- 1/(n_samples*lambda^2)
```
Now let's make the plot object using **ggplot**, after some heavy reading of the ggplot help page:

```{r}
g <- ggplot(data = data.frame(mu), aes(x=mu)) +
  geom_histogram(aes(y=..density..), binwidth=0.1, fill='lightblue', colour='black') +
  geom_density(colour="brown") + stat_function(fun=dnorm, colour="red", size=1,
             args = list(mean = 5,sd = 1/(lambda)*(1/sqrt(n_samples))))
```

Now we plot these to verify how "normal" they are. Note the red distribution is a normal distribution with mean 5 and standard deviation defined above, and the brown curve is the fitted exponential. This shows that it indeed approaches normality.

```{r}
plot(g)
```

We can also can confirm this with a Shapiro-Wilkins test:
```{r}
shapiro <- shapiro.test(mu)$p.value # answer is 2.208415e-12
```
The distribution is also centered on 5. Now let's take a look at the confidence interval for 1/lambda.


```{r}
lambda_val <- seq(0.1, 100.0, by = .5)
coverage <- sapply(lambda_val, function(lambda){
  runs   <- matrix(rexp(n_samples*n_sims,lambda) , n_sims)    
  lhats  <- apply(runs , 1, mean)
  lsd    <- apply(runs,1,sd)
  ll     <- lhats - qnorm(.975) * lsd /sqrt(n_samples)
  ul     <- lhats + qnorm(.975) * lsd /sqrt(n_samples)
  mean(ll < 1/lambda & ul > 1/lambda)

  })

# plot all the things

ggplot(data.frame(lambda_val, coverage), aes(x=lambda_val, y=coverage)) +  
    geom_line(size = .25) + geom_hline(yintercept = 0.95) + 
    geom_hline(yintercept = 0.925, colour='red', linetype=2)+
    ylim(.85, 1.0) +  xlab("Lambda") +  
    ggtitle("Coverage of 95% intervals")
```

We seem to have a 92.5% coverage for the 95% confidence intervals of sample size 40. Lambda does not affect the coverage.

















